Verifying Demonstrations

### 2018-10-31 paper/intro.tex

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.
\sonja{add (sub) sections for performance and verification}

>>>>

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.
\sonja{add (sub) sections for performance and verification}

### 2018-10-31 paper/system-model.tex

We will now describe our system and adversary models.
We first present an abstraction of a protest and how to count the participation 
(\cref{protest-model}) and the desired verifiabiltiy properties 
(\cref{verifiability-properties}).
Next, we present the communication and adversary model (\cref{adversary-model}) 
together with the desired privacy properties (\cref{privacy-properties}).

\include*{protest-model}
\include*{verifiability-properties}
\include*{adversary-model}
\include*{privacy-properties}

>>>>

To set the stage, we will now describe our system model including assumptions
(\cref{assumptions}) and present an abstraction of a protest and how to
count the participation (\cref{protest-model}). We then formulate the desired verifiability
(\cref{verifiability-properties}) and privacy properties
(\cref{privacy-properties}) and adversary model (\cref{adversary-model}).

\subsection{System model and physical assumptions}
\label{assumptions}

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}.

In practical terms, participants witness each other's participation
using their smartphones (or similar devices) running the protocol
described in \cref{Protocol} and uploading their testimony (\ie, proof
shares) to a ledger (such as a blockchain) after the protest. 
During the protest, the devices might be limited by their batteries in
terms of the computations they can perform and only have local connectivity to each other.
No connection to any global network such as the Internet is
necessary during this time.  
Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie, Internet connections) and are not computationally limited by any battery.
\sonja{another place to put reasons? Or if here, then for all
  assumptions. ``We need global connectivity before to read the head from the blockchain.
We need global connectivity after to upload the proof shares to the blockchain.''}

\include*{protest-model}
\include*{verifiability-properties}
\include*{privacy-properties}
\subsection{Adversary model}
\label{adversary-model}
